---
title: "Phylogenetic Comparative Analysis Package and Vignette"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Phylogenetic Comparative Analysis Package and Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
*Collaborators: Savvy Cornett & Jyhreh Johnson*

## Background
Phylogenetic Comparative Analysis or Phylogenetic Comparative Methods (PCMs) are a set of statistical methods that are used by biologist, geneticist, and anthropologists to analyze phylogenetic trees and track/presents species traits (Pennell & Harmon, 2013).\

## Introduction
In this package, we have included a dataset for the Sonic Hedgehog vertebrate orthologs (SHH_orthologs.csv) from the NIH database. We also have two functions: one for making a phylogenetic tree, and the other for doing a phylogenetic scatterplot.\

```{r Preliminaries, message=FALSE, warning=FALSE}
require(tidyverse)
require(rentrez)
require(devtools)
require(usethis)
require(devtools)
require(roxygen2)
require(withr)
```

```{r}
f_name <- "https://raw.githubusercontent.com/jyhrehjohnson/cornett-johnson_ADA_GroupProject/main/SHH_orthologs.csv"

sonic <- read_file(f_name)
```
## References\ 
Pennell, M. W., & Harmon, L. J. (2013). An integrative view of phylogenetic comparative methods: Connections to population genetics, community ecology, and paleobiology: Integrative comparative methods. Annals of the New York Academy of Sciences, 1289(1), 90–105. <https://doi.org/10.1111/nyas.12157>\
